---
title: "Assignment 4"
output:
  html_document:
    df_print: paged
---

Bavalan Thangarajah
1002194564
thanga29 

9a)


```{r}
library(tidyverse)
library(smmr)
```

```{r}
myurl="http://www.utsc.utoronto.ca/~butler/c32/nbapoints.csv"
NBA=read_csv(myurl)
NBA
```
 I have data that contains the date of an NBA game and number of points scored on that day under the new rules.

b) 
```{r}
ggplot(NBA,aes(x=Date,y=Points))+geom_boxplot()

```
 
c) The data within each date follow the line well so its distributed well.However there are many outliers, so the normality is questionable.Hence a one-sample t-test is best to determine if the increase of points scored in each game has increased. Since we are looking for improvement, the one-sample t-test is best.

d)
```{r}
t.test(NBA$Points, mu=183.2)
```
The average of points scored before 1999 is 183.2. After new rules have been placed the average of points scored is 195.88. Since the p-value is equal to 0.004575 it is less than 0.05 so therefore we reject the null hypothesis. Hence the speed of the game has not increased.

10a)

```{r}
myurl="https://www.utsc.utoronto.ca/~butler/c32/salaryinc.txt"
Salary=read_delim(myurl," ")
Salary
```

The data contains an Employee Letter and their 2 salaries from Jan 2016 and Jan 2017.

b)

A matched-pairs test is better because you are comparing the 2 salaries for an invididual employee. A two t-test is better if you are comparing 2 employees. However since you are comparing the two salaries of an invididual employee, a matched-pairs test is better.

c)

```{r}
Salary = Salary %>% mutate(diff=jan2017-jan2016)
Salary
```
```{r}
ggplot(Salary,aes(sample=diff))+stat_qq()+stat_qq_line()
```


Most of the plots follow the line however there are many outliers, so the normality is questionable.

d)

```{r}
with(Salary,t.test(jan2017,jan2016,paired=T))
```

That the average increase of salaries from 2016-2017 is 6.185 thousand dollars. Also since the p-value is very small of 2.271e-09 which is less 0.05 we reject the null hypothesis.

e)

```{r}
t.test(Salary$diff,conf.level = 0.95)
```

With 95% confidence interval the increase of salaries from 2016-2017 is between 4.902231 - 7.467769 thousand dollars. The average of salary increase is 6.185 thousand dollars. The CEO should look at where it says "95 percent confidence interval:" to get a range of how much the salaries increased. He should also look at where it says "mean of x" to get the average salary increase.